Reading Notes

### 2020-07-13 paper.tex
finished and added new paper to bib

\cite{Marsh2014}

@@

>>>>

\cite{Marsh2014}
coarse grain simulations of thiophene polymers (3 site model). changing the spacing and regioregularity of the side chains results in different morphologies and can be related to different real compounds.
orientation of side chains along the backbone is more significant than side chain density, side chain-side chain interactions, or side chain length. side chains on boths sides form lamellae--on one side form hexagonally packed cylinder which can transition at low temp to lamellae or ribbons depending on side chain interaction strength. interaction strength affects order-disorder transition temperature (ODT) stronger attraction=higher ODT. side chain length modulates the spacing between features such as cylinders or lamellae.
mentions atomistic and 1 site model of p3ht. atomistic does not access time scales long enough to observe lamellae formation. 1 site model couldn't see lamellae probably because there are no side chains.
The CG model parameter are obtained in ref 29 added below. LJ potential is used for nonbonded. Harmonic bonding used.

\cite{Schwarz2013}
read this with the intention of understanding how the CG potentials were derived.

@@

\cite{li2020}
excited to read this! Andrew White was Rainier's advisor.
